Fig1

### 2020-05-06 analysis/figure-1.Rmd
better fig 1

```

@@

b <- plottsneelipse(chartsne, chartsne$tissue, allcolors)   + labs(y = "tSNE 2 ", subtitle = " ")  
c <- plottsneelipse(chartsne, chartsne$sex, allcolors)   + labs(y = "tSNE 2 ", subtitle = " ")

d1 <- sexbarplots(hypsex, 0, 7100) + labs(y = "DEGS", subtitle = "hypothalamus" )
d2 <- sexbarplots(pitsex, 0, 7100) + labs(subtitle = "pituitary" ) + 
  theme(axis.text.y = element_blank(), axis.line.y = element_blank(), axis.ticks = element_blank())
d3 <- sexbarplots(gonsex, 0, 7100) + labs(subtitle = "gonads" ) +
  theme(axis.text.y = element_blank(), axis.line.y = element_blank(), axis.ticks = element_blank())

e <- plottsneelipsev2(hyptsne, hyptsne$treatment, allcolors) + 
  labs(x = NULL, subtitle = "hypothalamus")  + 
  facet_wrap(~sex, scales = "free")

g <- plottsneelipsev2(pittsne, pittsne$treatment, allcolors ) + 
  labs(x = NULL, subtitle = "pituitary") + 
  facet_wrap(~sex, scales = "free") +
  theme(strip.text = element_blank())

i <- plottsneelipsev2(gontsne, gontsne$treatment, allcolors ) + 
   facet_wrap(~sex, scales = "free") +
  theme(strip.text = element_blank()) +
  labs(x = "tSNE1 \n \n \n \n", subtitle = "gonads")

# hyp
f <- makebargraph("hypothalamus","DEGs", 0, 4300) + 
  theme(axis.text.x = element_blank(), 
        axis.title.x = element_blank())  +
  labs(subtitle = "hypothalamus")
# pit
h <- makebargraph("pituitary","DEGs", 0, 4300)  +  
  theme(axis.text.x = element_blank(), 
        axis.title.x = element_blank(), 
        strip.text.x = element_blank())  +
  labs(subtitle = "pituitary")
# gon
j <- makebargraph("gonad","DEGs", 0, 4300) +  
  theme(strip.text.x = element_blank()) +
  scale_x_discrete(labels = comparisonlabels)+
  labs(subtitle = "gonads")

bcd <- plot_grid(b,c,d1,d2,d3, nrow = 1, labels = c("B", "C", "D"), 
                   label_size = 8, rel_widths = c(1.2,1.2,1.2,1,1))

etoj <- plot_grid(e,f,g,h,i,j, ncol = 2, rel_heights = c(1,1,1.4), rel_widths = c(2.4,3.2),
                  labels = c("E", "F", "G", "H", "I", "J"), label_size = 8)

fig1 <- plot_grid(a, bcd, etoj, nrow = 3, rel_heights = c(0.8,0.7,2),
                  labels = c("A"), label_size = 8)
fig1
```

>>>>

hyppit <- read_csv("../results/DEseq2/tissue/hypothalamus_pituitary_DEGs.csv") 
hypgon <- read_csv("../results/DEseq2/tissue/hypothalamus_gonad_DEGs.csv")
pitgon <- read_csv("../results/DEseq2/tissue/pituitary_gonad_DEGs.csv")

hyppit$direction <- factor(hyppit$direction, levels = c("hypothalamus", "pituitary"))
hypgon$direction <- factor(hypgon$direction, levels = c("hypothalamus",  "gonad"))
pitgon$direction <- factor(pitgon$direction, levels = c( "pituitary", "gonad"))
```

@@

b1 <- plottsneelipse(chartsne, chartsne$tissue, allcolors)   + labs(y = "tSNE 2 ", subtitle = " ")  
b2 <- sexbarplots(hyppit, 0, 8100) + labs(subtitle = " ", y = "DEGs w/ + LFC") +
  theme(axis.text.y = element_blank(), axis.ticks = element_blank()) +
  scale_x_discrete(labels=c("hypothalamus" = "hyp", "pituitary" = "pit" ))
b3 <- sexbarplots(hypgon, 0, 8100) + labs(subtitle = " " ) +
  theme(axis.text.y = element_blank(), axis.line.y = element_blank(), 
        axis.ticks = element_blank(), axis.title.y = element_blank()) +
    scale_x_discrete(labels=c("hypothalamus" = "hyp",  "gonad" = "gon"))
b4 <- sexbarplots(pitgon, 0, 8100) + labs(subtitle = " " ) +
  theme(axis.text.y = element_blank(), axis.line.y = element_blank(),  
        axis.ticks = element_blank(), axis.title.y = element_blank()) +
    scale_x_discrete(labels=c(  "pituitary" = "pit", "gonad" = "gon"))

c1 <- plottsneelipse(chartsne, chartsne$sex, allcolors)   + labs(y = "tSNE 2 ", subtitle = " ")    
c2 <- sexbarplots(hypsex, 0, 8100) + labs(y = "DEGs w/ + LFC", subtitle = "hypothalamus" ) +
  theme(axis.text.y = element_blank(), axis.ticks = element_blank())
c3 <- sexbarplots(pitsex, 0, 8100) + labs(subtitle = "pituitary" ) + 
  theme(axis.text.y = element_blank(), axis.line.y = element_blank(),  
        axis.ticks = element_blank(), axis.title.y = element_blank())
c4 <- sexbarplots(gonsex, 0, 8100) + labs(subtitle = "gonads" ) +
  theme(axis.text.y = element_blank(), axis.line.y = element_blank(),  
        axis.ticks = element_blank(), axis.title.y = element_blank())

d1 <- plottsneelipsev2(hyptsne, hyptsne$treatment, allcolors) + 
  labs(x = NULL, subtitle = "hypothalamus")  + 
  facet_wrap(~sex, scales = "free")

d3 <- plottsneelipsev2(pittsne, pittsne$treatment, allcolors ) + 
  labs(x = NULL, subtitle = "pituitary") + 
  facet_wrap(~sex, scales = "free") +
  theme(strip.text = element_blank())

d5 <- plottsneelipsev2(gontsne, gontsne$treatment, allcolors ) + 
   facet_wrap(~sex, scales = "free") +
  theme(strip.text = element_blank()) +
  labs(x = "tSNE1 \n \n DEGs = differentially expressed genes \n + LFC = positive log fold change", 
       subtitle = "gonads")

# hyp
d2 <- makebargraph("hypothalamus","DEGs w/ + LFC", 0, 4300) + 
  theme(axis.ticks = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_blank())  +
  labs(subtitle = " ")
# pit
d4 <- makebargraph("pituitary","DEGs w/ + LFC", 0, 4300)  +  
  theme(axis.ticks = element_blank(),
        axis.text.x = element_blank(), 
        axis.text.y = element_blank(),
        axis.title.x = element_blank(), 
        strip.text.x = element_blank())  +
  labs(subtitle = " ")
# gon
d6 <- makebargraph("gonad","DEGs w/ + LFC", 0, 4300) +  
  theme(axis.ticks = element_blank(),
        axis.text.y = element_blank(),
        strip.text.x = element_blank()) +
  scale_x_discrete(labels = comparisonlabels)+
  labs(subtitle = " ")

bc <- plot_grid(b1,b2,b3,b4, c1,c2,c3,c4, nrow = 1, rel_widths = c(1.5,1.1,0.9,0.9,1.5,1.1,0.9,0.9),
                labels = c("B", "", "", "", "C"), label_size = 8)

d <- plot_grid(d1,d2,d3,d4,d5,d6, ncol = 2, rel_heights = c(1,0.9,1.3), rel_widths = c(1,2),
                  labels = c("D"), label_size = 8)

fig1 <- plot_grid(a,bc, d, nrow = 3, rel_heights = c(0.7,0.7,2),
                  labels = c("A"), label_size = 8)
fig1
```
